\documentclass[10pt]{article}

\usepackage{calc}

\reversemarginpar

\usepackage[paper=a4paper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=1.2in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=0.75in,               % 1 inch margins
            includemp]{geometry}

%\usepackage[paper=a4paper,
%            %includefoot, % Uncomment to put page number above margin
%            marginparwidth=30.5mm,    % Length of section titles
%            marginparsep=1.5mm,       % Space between titles and text
%            margin=25mm,              % 25mm margins
%            includemp]{geometry}

\setlength{\parindent}{0in}

\usepackage{paralist}

\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
%\pagestyle{empty}      % Remove page numbering
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                    \arabic{page} of \protect\pageref*{LastPage} % +LP
%                    \arabic{page}                               % -LP
                    \hfill \,}}

\usepackage{color,hyperref}
\definecolor{black}{rgb}{0.0,0.0,0.0}
\hypersetup{colorlinks,breaklinks,
            linkcolor=black,urlcolor=black,
            anchorcolor=black,citecolor=black}

\newcommand{\makeheading}[1]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
                {\large \bfseries #1}\\[-0.15\baselineskip]%
                 \rule{\columnwidth}{1pt}%
         \end{minipage}}

\renewcommand{\section}[2]%
        {\pagebreak[2]\vspace{1.3\baselineskip}%
         \phantomsection\addcontentsline{toc}{section}{#1}%
         \hspace{0in}%
         \marginpar{
         \raggedright \scshape #1}#2}

\newenvironment{outerlist}[1][\enskip\textbullet]%
        {\begin{enumerate}[#1]}{\end{enumerate}%
         \vspace{-.6\baselineskip}}

\newenvironment{lonelist}[1][\enskip\textbullet]%
        {\vspace{-\baselineskip}\begin{list}{#1}{%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}

\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{compactenum}[#1]}{\end{compactenum}}

\newcommand{\blankline}{\quad\pagebreak[2]}

\begin{document}
\makeheading{Chris Lowder}

\section{Contact}
\newlength{\rcollength}\setlength{\rcollength}{3.0in}%
%
\begin{tabular}[t]{@{}p{\textwidth-\rcollength}p{\rcollength}}
\href{https://www.dur.ac.uk/mathematical.sciences/}{Mathematical Sciences}
                           & \textit{Mobile:} +44 (0) 7497 356988\\
\href{https://www.dur.ac.uk}{Durham University}
                           & \textit{Office:} ~+44 (0) 191 334 3087\\
Durham, DH1 3LE, United Kingdom    & \textit{E-mail:} \href{mailto:chris.lowder@durham.ac.uk}{chris.lowder@durham.ac.uk}
\end{tabular}

\section{Education}
\href{http://www.montana.edu/}{\textbf{Montana State University}},
Bozeman, Montana, United States
\begin{outerlist}
\setlength\itemsep{0em}
\item[] PhD
	\href{http://www.physics.montana.edu/}
	     {Physics}, June 2015
	     %GPA : 3.95 / 4.00\\
\item[] M.S.
	\href{http://www.physics.montana.edu/}
	     {Physics}, May 2011\\
\end{outerlist}

\href{http://www.gatech.edu/}{\textbf{Georgia Institute of Technology}}, 
Atlanta, Georgia, United States
\begin{outerlist}
\item[] B.S., 
        \href{http://www.physics.gatech.edu/}
             {Physics}, December 2007
	     %GPA : 3.84 / 4.00        
\end{outerlist}

\section{Publications}
\hangindent=0.2cm \href{http://adsabs.harvard.edu/abs/2014ApJ...783..142L}{Lowder, C., Qiu, J., Leamon, R. \& Liu, Y. \textit{Measurements of EUV Coronal Holes and Open Magnetic Flux.} ApJ 783, 142 (2014).}

\hangindent=0.4cm Lowder, C., Qiu, J., \& Leamon, R. \textit{Coronal Holes and Open Magnetic Flux over Cycles 23 and 24}. (accepted)

\hangindent=0.4cm Lowder, C., Qiu, J., Leamon, R., \& Longcope, D.  \textit{Connecting Coronal Holes and Open Magnetic Field}. (in preparation).

\hangindent=0.4cm Lowder, C., Qiu, J., \& Leamon, R., \textit{Transient Coronal Dimmings and connection to Heliospheric Open Flux}. (in preparation).

\hangindent=0.4cm Lowder, C., Yeates, A., \textit{Magnetic Flux Rope Identification and Characterization from\break Observationally-Driven Solar Coronal Models}. (in preparation).

\section{Conference Proceedings}
\hangindent=0.4cm \textit{Magnetic Flux Rope Identification and Characterization from Observationally-Driven Solar Coronal Models} UK National Astronomy Meeting (2016).

\hangindent=0.4cm \textit{Connecting Coronal Holes and Open Magnetic Field via Numerical Modeling and Observations.} Triennial Earth-Sun Summit  / SPD (2015).

\hangindent=0.4cm \textit{A Comparison of EUV Coronal Hole Measurements and Modeled Open Magnetic Field -or- How I learned to stop worrying and love the potential magnetic field.} GSU Colloquium Series (2014).

\hangindent=0.4cm \textit{Full Surface Automated Coronal Hole Detection and Characterization to Constrain Global Magnetic Field Models}. AAS Meeting 220 (2012).

\hangindent=0.4cm \textit{Transient coronal holes : A statistical study of coronal dimming regions}. The Origin, Evolution, and Diagnosis of Solar Flare Magnetic Fields and Plasmas (2010).

\hangindent=0.4cm \textit{Coronal Mass Ejections : A Study of Structural Evolution and Classification}. AAS Meeting 210 (2007).

\section{Computing}
\textit{Proficient} : Python, IDL, \LaTeX, OpenMPI, Fortran

\textit{Familiar} : C++, Octave, MATLAB, OpenCL

Experience in large-scale parallel computing projects and databases

%\href{http://www.georgiasouthern.edu/}{\textbf{Georgia Southern University}}, 
%Statesboro, Georgia, United States
%\begin{outerlist}

%\item[] Post-Secondary Options Student / Joint Enrollment
%        \begin{innerlist}
%        \item GPA : 4.00 / 4.00
%        \end{innerlist}
        
%\end{outerlist}

\section{Research Experience}
\href{https://www.dur.ac.uk}{\textbf{Durham University}}, 
Durham, United Kingdom\\
\href{https://www.dur.ac.uk/mathematical.sciences/}{\textbf{Department of Mathematical Sciences}}
\begin{outerlist}
\item[] \textit{Postdoctoral Research Associate}%
        \hfill \textbf{August 2015 to Present}
\begin{innerlist}
  \item Working with \href{http://www.maths.dur.ac.uk/~bmjg46/}{Anthony Yeates} on modelling solar flux rope eruption and detection.
  \\
\end{innerlist}

\end{outerlist}


\href{http://www.montana.edu}{\textbf{Montana State University}}, 
Bozeman, Montana, United States\\
\href{http://www.physics.montana.edu}{\textbf{School of Physics}}
\begin{outerlist}
\item[] \textit{Graduate Research Assistant}%
        \hfill \textbf{August 2009 to August 2015}
\begin{innerlist}
  \item Worked with \href{http://solar.physics.montana.edu/qiuj/}{Dr. Jiong Qiu} and \href{http://solar.physics.montana.edu/leamon/}{Dr. Robert Leamon} in analyzing coronal dimming
  \item Designed automated code to detect and characterize coronal holes from SDO and STEREO EUV data to constrain global models of open magnetic field
  \item Developed flux transport model to study evolution of far-side open magnetic field
  \\
\end{innerlist}

\end{outerlist}

%\href{http://solar.physics.montana.edu/}{\textbf{Montana State University}}, 
%Bozeman, Montana, United States\\
%\href{http://solar.physics.montana.edu/}{\textbf{Solar Physics Group}}
%\begin{outerlist}
%\item[] \textit{NSF Summer REU Undergraduate Researcher}%
%        \hfill \textbf{June 2007 to August 2007}
%\begin{innerlist}
%
%  \item Improved methods to resolve the 180-degree ambiguity in solar vector \mbox{magnetograms}
%  \item Attempted to apply method to high resolution Hinode magnetograms
%  \\
%\end{innerlist}
%
%\end{outerlist}
%
%
%\href{http://www.ifa.hawaii.edu/}{\textbf{University of Hawai'i}}, 
%Honolulu, Hawai'i United States\\
%\href{http://www.ifa.hawaii.edu/}{\textbf{Institute for Astronomy}}
%\begin{outerlist}
%\item[] \textit{NSF Summer REU Undergraduate Researcher}%
%        \hfill \textbf{May 2006 to August 2006}
%\begin{innerlist}
%  \item Analysis of CMEs utilizing SOHO data for Dr. Shadia Habbal and Dr. Huw Morgan
%  \item Observational experience and interaction with astronomers at Mauna Kea \mbox{observatories} on the IRTF, Caltech CSO, and the UH 88'' \\
%\end{innerlist}
%
%\end{outerlist}

\end{document}
